### 2016-12-02 ms/ms.tex
version sent to ecol let

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage[numbers,sort&compress]{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{xr}
\externaldocument{SI}
\usepackage{url}
\usepackage{rotating}

\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

\newcommand{\flagged}[1] {
  \textcolor{blue}{#1}
}

@@

In a preferential attachment process, we expect that the most
persistent and high degree species (the species with the most unique
interaction partners) would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member in
across years in all the assembling hedgerows. Becaused species degree
and persistence were strongly correlated, it is difficult to
disentangle the causal mechanism for why species with those
characteristics are so variable in their network position. Species
that can interaction with a relativly high number of interaction
partners may be better able to exploit the limited floral resources in
the intensively managed agriculture landscape, and thus also be the
most persistent \citep[in ant-plant mutualisms,
][]{diaz2010changes}. More persistent species usually have longer
phenologies, so they can visit many different flowers, resulting in a
higher degree \citep{Vazquez2009, fort2016abundance}. Either way, our
result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on both the other pollinator species that are present
and the state of the plant community \citep{macleod2016measuring,
  gomez2006ecological, Waser1996}. Thus given the opportunity and
ability to use different resources, species will often change their
network positions \citep{macleod2016measuring}.

@@

% The relationship between diversity and stability in networks
% has been the subject of considerable debate
% \citep[e.g.,][]{may1972will, pimm1984complexity,
%   montoya2006ecological}. Our results provide one of the few empirical
% examples of how restoring species diversity contributes to enhancing
% network stability.

% providing further evidence that hedgerows are a valuable tool for
% promoting species conservation and ecosystem provision in agricultural
% areas \citep{mgonigle-2015-x, ponisio2015farm,
%   kremen-2015-602}.

In general, plant-pollinator networks are highly dynamic, with high
turnover of species and interactions both within and between seasons
\citep{Burkle2011}. Though our non-assembling communities experienced
fewer network reorganizations than the assembling hedgerows, $82\%$ of
field margins and $40\%$ of mature hedgerows underwent at least one
changing point in network structure. Pollinators are also highly
opportunistic \citep{petanidou-2008-564, Vazquez2005b,
  albrecht2010plant}, though trait complementarity such as tongue
length and corolla depth impose some biophysical limits to the
interactions between plants and pollinators
\citep{Vazquez2009evaluating, Vazquez2009, Stang2009, Stang2006,
  Santamaria2007}. Such opportunism may buffer plant-pollinator
communities from global change \citep[e.g.,][]{ramos2012topological,
  kaiser2010robustness}, but our limited understanding of the assembly
of these communities impedes making such predictions
\citep{Vazquez2009, Burkle2011}. Unlike in the broader food web
literature, we have few assembly models of mutualistic network
assembly \citep{valdovinos2013adaptive, Nuismer2013, Guimaraes2011}.
In addition, the few developed models often borrow their mechanisms
from competitive interactions, leading to inaccurate biological
assumptions \citep{holland2006comment}. We need further development of
mechanistic models of mutualistic systems to generate testable
predictions, along with empirical exploration of network
assembly. Plant-pollinator communities and mutualisms are vital for
biodiversity maintenance and essential ecosystem service provision. We
must therefore understand the processes underlying their assembly to
facilitate restoration and conservation.

@@

\bibliographystyle{ecol_let}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/changePoint/plotting/networksv1.pdf}
  \caption{Assembling hedgerow networks had more changing points
    (vertical red lines) than non-assembling hedgerows and weedy field
    margins (a representative sample of non-assembling sites are
    depicted here). In each network, plants and pollinators are
    represented by green and yellow circles, respectively, weighted by
    their degree. Each species has a consistent position in the
    perimeter of the network across years. Asterisks indicate the year
    the hegdgerow was planted. Before that, the sites were weedy field
    margins.}
  \label{fig:changePoints}
\end{figure}
\clearpage

\begin{sidewaysfigure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky3.pdf}
  \caption{The species module membership between network changing
    points. Two representative assembling hedgerows are depicted. In
    the top panel, species are grouped by module. The bottom panels
    visualize the flow of species between modules between changing
    points. Each line represents the change of s species from one
    module to another. }
  \label{fig:changePoints2}
\end{sidewaysfigure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/networkLevel/figures/baci.pdf}
  \caption{Nestedness, plant richness and pollinator richness
    increased as the networks assembled. Specialization and modularity
    remained consistent across years, while connectance decreased. The
    nestedness, modularity and specialization scores represent
    $z$-scores. Scores greater than $\sim 2$ or less than $\sim -2$
    are significantly more or less structured than randomly assembled
    networks. Points are the metric value for each site at each year
    of assembly. The solid line indicates the mean slope estimate and
    the dashed lines are the $95\%$ confidence intervals around the
    estimate.}
  \label{fig:baci}
\end{figure}
\clearpage

>>>>

\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}
\usepackage[numbers]{natbib}
% \usepackage{natbib}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{mathpazo}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{array}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{times}
\usepackage{textcomp}
\usepackage{xr}
\usepackage{etoolbox}
\usepackage{filecontents}
\usepackage{url}
\usepackage{rotating}
\externaldocument{SI}

\makeatletter
\def\@biblabel#1{#1.\\}
\makeatother

\bibliographystyle{ecology_let}

\parindent=2em
\setlength{\parskip}{1ex}

\RequirePackage{lineno}

@@

In a preferential attachment process, we expect that the most
persistent and high degree species (the species with the most unique
interaction partners) would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member in
across years in all the assembling hedgerows. Because species degree
and persistence were strongly correlated, it is difficult to
disentangle the causal mechanism for why species with those
characteristics are so variable in their network position. Species
that can interact with a relatively high number of partners may be
better able to exploit the limited floral resources in the intensively
managed agriculture landscape, and thus also be the most persistent
\citep[in ant-plant mutualisms, ][]{diaz2010changes}. More persistent
species usually have longer phenologies, so they can visit many
different flowers, resulting in a higher degree \citep{Vazquez2009,
  fort2016abundance}. Either way, our result suggests that adaptable
species can change their network position to utilize the most
advantageous floral resources available, which may depend on both the
other pollinator species that are present and the state of the plant
community \citep{Waser1996, gomez2006ecological,
  macleod2016measuring}. Thus given the opportunity and ability to use
different resources, species will often change their network positions
\citep{macleod2016measuring}.

@@

In general, plant-pollinator networks are highly dynamic, with high
turnover of species and interactions both within and between seasons
\citep{Burkle2011}. Though our non-assembling communities experienced
fewer network reorganizations than the assembling hedgerows, $82\%$ of
field margins and $40\%$ of mature hedgerows underwent at least one
changing point in network structure. Pollinators are highly
opportunistic \citep{petanidou-2008-564, Vazquez2005b,
  albrecht2010plant}, though trait complementarity such as tongue
length and corolla depth impose some biophysical limits to the
interactions between plants and pollinators \citep{Stang2006,
  Santamaria2007, Vazquez2009evaluating, Vazquez2009, Stang2009}. Such
opportunism may buffer plant-pollinator communities from global change
\citep[e.g.,][]{ramos2012topological, kaiser2010robustness}, but our
limited understanding of the assembly of these communities impedes
making such predictions \citep{Vazquez2009, Burkle2011}. Unlike in the
broader food web literature, we have few assembly models of
mutualistic network assembly \citep{valdovinos2013adaptive,
  Nuismer2013, Guimaraes2011}.  In addition, the few developed models
often borrow their mechanisms from competitive interactions, leading
to inaccurate biological assumptions \citep{holland2006comment}. We
need further development of mechanistic models of mutualistic systems
to generate testable predictions, along with empirical exploration of
network assembly. Plant-pollinator communities and mutualisms are
vital for biodiversity maintenance and essential ecosystem service
provision. We must therefore understand the processes underlying their
assembly to facilitate restoration and conservation.

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/changePoint/plotting/networksv1.pdf}
  \caption{Assembling hedgerow networks had more changing points
    (vertical red lines) than non-assembling hedgerows and weedy field
    margins (a representative sample of non-assembling sites are
    depicted here). In each network, plants and pollinators are
    represented by green and yellow circles, respectively, weighted by
    their degree. Each species has a consistent position in the
    perimeter of the network across years. Asterisks indicate the year
    the hedgerow was planted. Before that, the sites were weedy field
    margins.}
  \label{fig:changePoints}
\end{figure}
\clearpage

\begin{sidewaysfigure}
  \centering
  \includegraphics[width=.95\textwidth]{../analysis/changePoint/plotting/communitiesSkanky3.pdf}
  \caption{The species module membership between network changing
    points. Two representative assembling hedgerows are depicted. In
    the top panel, species are grouped by module. The bottom panels
    visualize the flow of species to different modules between change
    points. }
  \label{fig:changePoints2}
\end{sidewaysfigure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=1\textwidth]{../analysis/networkLevel/figures/baci.pdf}
  \caption{Plant richness and pollinator richness increased as the
    networks assembled. Nestedness, modularity and specialization did
    not change predictable across years, while connectance
    decreased. The nestedness, modularity and specialization scores
    represent $z$-scores. Scores greater than $\sim 2$ or less than
    $\sim -2$ are significantly more or less structured than randomly
    assembled networks. Points are the metric value for each site at
    each year of assembly. The solid line indicates the mean slope
    estimate and the dashed lines are the $95\%$ confidence intervals
    around the estimate.}
  \label{fig:baci}
\end{figure}
\clearpage
